taxize - taxonomic search and retrieval in R

### 2013-06-21 inst/doc/taxize_withcode_plos.Rnw
added table fixes #155

%% ** EDIT HERE **
%% PLEASE INCLUDE ALL MACROS BELOW
\usepackage{hyperref}

%% END MACROS SECTION

@@

\begin{table}[!ht]
\caption{
\bf{Data sources used in taxize, tasks available, and links to them}}
\begin{tabular}{|l|c|c|c|c|}
\hline
Source name & Name search & Name resolution & Phylogeny & Sequences  \\
\hline
Encyclopedia of Life \cite{eol} & Yes & See GNR below & No & No \\
Integrated Taxonomic Information System \cite{itis} & Yes & Synonyms & No & No \\
iPlant Taxonomic Name Resolution Service \cite{tnrs} & Yes & Yes & No & No \\
Phylomatic \cite{webb2005} & No & No & Yes & No \\
uBio \cite{ubio} & Yes & Yes & No & No \\
Global Names Resolver \cite{eolgnr} & Yes & Yes & No & No \\
Global Names Index \cite{eolgnr} & Yes & No & No & No \\
IUCN Red List \cite{iucn} & Yes & No & No & No \\
Tropicos \cite{tropicos} & Yes & Yes & No & No \\
Plantminer \cite{carvalho2010plantminer} & Yes & No & No & No \\
The Plant List & Yes & Yes & No & No \\
Catalogue of Life \cite{col} & Yes & Yes & No & No \\
National Center for Biotechnology Information \cite{federhen} & Yes & X & Yes \textsuperscript{a} & Yes \\
\hline
\end{tabular}
\begin{flushleft}\textsuperscript{a} Web only, no API, see \url{http://1.usa.gov/11R446a}
\end{flushleft}
\label{tab:a}
\end{table}

>>>>

%% ** EDIT HERE **
%% PLEASE INCLUDE ALL MACROS BELOW
\usepackage{hyperref}
\usepackage{array}

\newcolumntype{L}{>{\raggedright\arraybackslash}m{5cm}} % creates now column type to wrap text
\newcolumntype{B}{>{\raggedright\arraybackslash}m{3cm}} % creates now column type to wrap text
\newcolumntype{C}{>{\raggedright\arraybackslash}m{3.5cm}} % creates now column type to wrap text
\newcolumntype{D}{>{\raggedright\arraybackslash}m{2.5cm}} % creates now column type to wrap text
%% END MACROS SECTION

@@

% \begin{table}[!ht]
% \caption{
% \bf{Data sources used in taxize, tasks available, and links to them}}
% \begin{tabular}{|l|c|c|c|c|}
% \hline
% Source name & Name search & Name resolution & Phylogeny & Sequences  \\
% \hline
% Encyclopedia of Life \cite{eol} & Yes & See GNR below & No & No \\
% Integrated Taxonomic Information System \cite{itis} & Yes & Synonyms & No & No \\
% iPlant Taxonomic Name Resolution Service \cite{tnrs} & Yes & Yes & No & No \\
% Phylomatic \cite{webb2005} & No & No & Yes & No \\
% uBio \cite{ubio} & Yes & Yes & No & No \\
% Global Names Resolver \cite{eolgnr} & Yes & Yes & No & No \\
% Global Names Index \cite{eolgni} & Yes & No & No & No \\
% IUCN Red List \cite{iucn} & Yes & No & No & No \\
% Tropicos \cite{tropicos} & Yes & Yes & No & No \\
% Plantminer \cite{carvalho2010plantminer} & Yes & No & No & No \\
% The Plant List & Yes & Yes & No & No \\
% Catalogue of Life \cite{col} & Yes & Yes & No & No \\
% National Center for Biotechnology Information \cite{federhen} & Yes & X & Yes \textsuperscript{a} & Yes \\
% \hline
% \end{tabular}
% \begin{flushleft}\textsuperscript{a} Web only, no API, see \url{http://1.usa.gov/11R446a}
% \end{flushleft}
% \label{tab:a}
% \end{table}

\begin{table}[!ht]
\caption{
\bf{Some key functions in taxize, what they do, and their data sources}}
\begin{tabular}{|l|L|L|}
\hline
Function name & What it does & Source \\
\hline
apg\_lookup & Changes names to match the APGIII list & Angiosperm Phylogeny Group \cite{apgiii}  \\
classification & Upstream classification & Various  \\
col\_children & Direct children & Catalogue of Life \cite{col}  \\
col\_downstream & Downstream taxa to specified rank & Catalogue of Life \cite{col}  \\
eol\_hierarchy & Upstream classification & Encyclopedia of Life \cite{eol}  \\
eol\_search & Search EOL taxon information & Encyclopedia of Life \cite{eol}  \\
get\_seqs & Get NCBI sequences & National Center for Biotechnology Information \cite{federhen}  \\
get\_tsn & Get ITIS TSN & Integrated Taxonomic Information System \cite{itis}  \\
get\_uid & Get NCBI UID & National Center for Biotechnology Information \cite{federhen}  \\
searchbycommonname & Search ITIS by common name & Integrated Taxonomic Information System \cite{itis}  \\
searchbyscientificname & Search ITIS by scientific name & Integrated Taxonomic Information System \cite{itis}  \\
gisd\_isinvasive & Inasiveness status & Global Invasive Species Database \cite{gisd}  \\
gni\_parse & Parse scientific names into components & Global Names Index \cite{eol,eolgni}   \\
gni\_search & Search EOL's global names index & Global Names Index \cite{eol,eolgni}   \\
gnr\_resolve & Resolve names using EOL's global names index & Global Names Resolver \cite{eol,eolgnr}  \\
itis\_downstream & Downstream taxa to specified rank & Integrated Taxonomic Information System \cite{itis}  \\
iucn\_status & IUCN status & IUCN Red List \cite{iucn}  \\
phylomatic\_tree & Get a plant Phylogeny & Phylomatic \cite{webb2005}  \\
plantminer & Search Plantminer & Plantminer \cite{carvalho2010plantminer}   \\
tax\_name & Get taxonomic name for specific rank & Various  \\
tax\_rank & Get rank of a taxonomic name & Various  \\
tnrs & Resolve names using iPlant & iPlant Taxonomic Name Resolution Service \cite{tnrs}  \\
tp\_acceptednames & Check for accepted names using Tropicos & Tropicos \cite{tropicos}  \\
tpl\_search & Search the Plant List & The Plant List \cite{theplantlist}  \\
ubio\_namebank & Search uBio & uBio \cite{ubio}  \\
\hline
\end{tabular}
\label{tab:a}
\end{table}

### 2013-06-21 inst/doc/taxize_withcode_plos.tex
added table fixes #155

%% ** EDIT HERE **
%% PLEASE INCLUDE ALL MACROS BELOW
\usepackage{hyperref}

%% END MACROS SECTION
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}

>>>>

%% ** EDIT HERE **
%% PLEASE INCLUDE ALL MACROS BELOW
\usepackage{hyperref}
\usepackage{array}

\newcolumntype{L}{>{\raggedright\arraybackslash}m{5cm}} % creates now column type to wrap text
\newcolumntype{B}{>{\raggedright\arraybackslash}m{3cm}} % creates now column type to wrap text
\newcolumntype{C}{>{\raggedright\arraybackslash}m{3.5cm}} % creates now column type to wrap text
\newcolumntype{D}{>{\raggedright\arraybackslash}m{2.5cm}} % creates now column type to wrap text
%% END MACROS SECTION
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
